### 2020-06-08 Research_[2020-05-18]_Piecewise_Monotone_Quintic_Fortran/paper/pmqsi20.tex
Added paper directory, all of this work may be moved into the papers repository soon.

% Algorithm XXX: DELAUNAYSPARSE---Interpolation via a sparse subset of
% the Delaunay triangulation in medium to high dimensions,
% Tyler H. Chang, Layne T. Watson, Thomas C.H. Lux, Ali R. Butt,
% Kirk W. Cameron, and Yili Hong,
% ACM Trans. Math. Software, ?/?/2018.
% 
%
\magnification=1000 \hsize=30pc \vsize=47pc
\parindent=10pt \parskip=0pt plus 3pt
\baselineskip=13pt plus 2pt minus 1pt \lineskiplimit=2pt
\lineskip=2pt plus 2pt                                  %\raggedright
\tolerance=800
%\abovedisplayskip=6pt plus 6pt minus 3pt
%\abovedisplayshortskip=0pt plus 3pt
%\belowdisplayskip=6pt plus 6pt minus 3pt
%\belowdisplayshortskip=6pt plus 2pt minus 3pt

@@

\def\leftrh{Chang et al.}
\def\rightrh{Algorithm XXX: DELAUNAYSPARSE}

{\baselineskip=24pt \leftline{\hlvXVIII Algorithm XXX: DELAUNAYSPARSE:}
\leftline{\hlvXVIII Interpolation via a Sparse Subset of the}
\leftline{\hlvXVIII Delaunay Triangulation in Medium to High}
\leftline{\hlvXVIII Dimensions}}
\bigskip\medskip
\leftline{\hlv TYLER H. CHANG, LAYNE T. WATSON, THOMAS C.H. LUX, ALI R. BUTT,}
\smallskip
\leftline{\hlv KIRK W. CAMERON, AND YILI HONG}
\smallskip
\leftline{\hlv Virginia Polytechnic Institute and State University}
\bigskip

\hrule\bigskip\smallskip \footnote{}{\hskip
-\parindent{\parindent=0pt\rmVIII Authors' addresses:
T. H. Chang, T. C. H. Lux, A. R. Butt, K. W. Cameron,
Department of Computer Science, L. T. Watson,
Departments of Computer Science, Mathematics, and Aerospace and Ocean
Engineering, Y. Hong, Department of Statistics, Virginia
Polytechnic Institute \& State University, Blacksburg, VA 24061;
e-mail: {\ttVIII thchang@vt.edu}. \xpar
% Permission to make digital/hard copy of
%part or all of this work for personal or classroom use is granted
%without fee provided that the copies are not made or distributed for
%profit or commercial advantage, the copyright notice, the title of
%the publication, and its date appear, and notice is given that
%copying is by permission of the ACM, Inc. To copy otherwise, to
%republish, to post on servers, or to redistribute to lists, requires
%specific permission and/or fee. \xpar\copyright\ 2018 by the
%Association for Computing Machinery, Inc. \xpar 
}}

% Abstract and Introduction
{\rmVIII\parindent=0pt DELAUNAYSPARSE contains both serial and
parallel codes written in Fortran 2003 (with OpenMP) for performing
medium- to high-dimensional interpolation via the Delaunay triangulation.
To accommodate the exponential growth in the size of the Delaunay
triangulation in high dimensions, DELAUNAYSPARSE computes only a
sparse subset of the complete Delaunay triangulation, as necessary for
performing interpolation at the user specified points. This paper includes
algorithm and implementation details, complexity and sensitivity analyses,
usage information, and a brief performance study.

@@

\medskip
General Terms: Algorithms, Computational Geometry, Documentation

\medskip
Additional Key Words and Phrases: Delaunay triangulation, interpolation,
multivariate approximation, high-dimensional data

>>>>

% Algorithm XXX: PMQSI---Piecewise monotone quintic spline interpolation,
% Thomas C.H. Lux, Layne T. Watson, Tyler H. Chang, Joshua Detwiler, 
% Kirk W. Cameron, and Yili Hong
% ACM Trans. Math. Software, ?/?/2018.
% 
%
\magnification=1000 \hsize=30pc \vsize=47pc
\parindent=10pt \parskip=0pt plus 3pt
\baselineskip=13pt plus 2pt minus 1pt \lineskiplimit=2pt
\lineskip=2pt plus 2pt                                  %\raggedright
\tolerance=800
%\abovedisplayskip=6pt plus 6pt minus 3pt
%\abovedisplayshortskip=0pt plus 3pt
%\belowdisplayskip=6pt plus 6pt minus 3pt
%\belowdisplayshortskip=6pt plus 2pt minus 3pt

@@

\def\leftrh{Chang et al.}
\def\rightrh{Algorithm XXX: PMQSI}

{\baselineskip=24pt \leftline{\hlvXVIII Algorithm XXX: PMQSI: Piecewise Monotone}
\leftline{\hlvXVIII Quintic Spline Interpolation}
\bigskip\medskip
\leftline{\hlv THOMAS C.H. LUX, LAYNE T. WATSON, TYLER H. CHANG, JOSHUA DETWILER,}
\smallskip
\leftline{\hlv KIRK W. CAMERON, AND YILI HONG}
\smallskip
\leftline{\hlv Virginia Polytechnic Institute and State University}
\bigskip

\hrule\bigskip\smallskip \footnote{}{\hskip
-\parindent{\parindent=0pt\rmVIII Authors' addresses:
T. C. H. Lux, T. H. Chang, J. Ditwiler, K. W. Cameron,
Department of Computer Science, L. T. Watson,
Departments of Computer Science, Mathematics, and Aerospace and Ocean
Engineering, Y. Hong, Department of Statistics, Virginia
Polytechnic Institute \& State University, Blacksburg, VA 24061;
e-mail: {\ttVIII tchlux@vt.edu}. \xpar
% Permission to make digital/hard copy of
%part or all of this work for personal or classroom use is granted
%without fee provided that the copies are not made or distributed for
%profit or commercial advantage, the copyright notice, the title of
%the publication, and its date appear, and notice is given that
%copying is by permission of the ACM, Inc. To copy otherwise, to
%republish, to post on servers, or to redistribute to lists, requires
%specific permission and/or fee. \xpar\copyright\ 2018 by the
%Association for Computing Machinery, Inc. \xpar 
}}

% Abstract and Introduction
{\rmVIII\parindent=0pt PMQSI contains a serial code written in Fortran
  1995 for constructing piecewise monotone quintic spline interpolants
  to data. Using sharp theoretical monotonicity constraints, first and
  second derivative estimates at data provided by a quadratic facet
  model are refined to produce a $C^2$ piecewise monotone interpolant.
  This paper includes algorithm and implementation details, complexity
  and sensitivity analyses, usage information, and a brief performance
  study.

@@

\medskip
General Terms: Algorithms, Monotonicity, Documentation

\medskip
Additional Key Words and Phrases: Quintic Spline, interpolation
